---
title: "Optimal Price based on location"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
  word_document: default
---

In this problem we are optimized the prices of a product based on the location of the store and also on the sheliving location
```{r}
library(ISLR)
library(dplyr)
library(gridExtra)
library(ggplot2)
# Importing selected three columns into safeBabies from Carseats Dataset
SafeBabies <- Carseats %>% select("Sales", "Price", "ShelveLoc")
```


```{r}
#Filtering the data into Good,Medium and Bad based on the shelve locaction
good <- filter(SafeBabies,ShelveLoc == 'Good')
medium <- filter(SafeBabies,ShelveLoc == 'Medium')
bad <- filter(SafeBabies,ShelveLoc == 'Bad')
View(bad)
```


```{r}
# Building a regression Model for sales with respect to price for car seats where the shelve location good

shgood<-good[order(good$Price),]
head(shgood)
Model1 <- lm(shgood$Sales ~ shgood$Price, data = shgood)
summary(Model1)


```

```{r}
# Based on the results of regression model and after finding the derivate we obtained the equation for optimal price for car seats where shelve location good
optimal_price_good = (0.065785 *55 - 17.968864)/(2 * -0.065785)
optimal_price_good

```



```{r}
#Finding the optimal price for change in production cost from 40$ to 85$
result <- vector("numeric", 40)
for(cost in 40:86) {
     optimised_results_good <- (0.065785 *cost - 17.968864)/(2 * -0.065785)
   result[cost - 40] <- optimised_results_good
}
head(result)
```

```{r}
#Combing both optimized price and change in cost and named it as optimized_price_good
price<- c(40:85)
optimized_price_good<-cbind.data.frame(result,price)
names(optimized_price_good)<-c('Optimized Price','Change in Cost')
```

```{r}
# Building a regression Model for sales with respect to price for car seats where the shelve location bad
bad1<-bad[order(bad$Price),]
head(bad1)
Model2 <- lm(bad1$Sales ~ bad1$Price, data = bad1)
summary(Model2)
```

```{r}
# Based on the results of regression model and after finding the derivate we obtained the equation for optimal price for car seats where shelve location bad
Optimum_price_bad = (0.05522 * 55 - 11.832984) / (2 * -0.05522)
Optimum_price_bad
```



```{r}
#Finding the optimal price for change in production cost from 40$ to 85$
result <- vector("numeric", 40)
for(cost in 40:86) {
     optimised_results_bad <- (0.05522 *cost - 11.832984)/(2 * -0.05522)
   result[cost - 40] <- optimised_results_bad
}
head(result)
```


```{r}
#optimised_results_bad.function()
price<- c(40:85)
optimized_prie_bad<-cbind.data.frame(result,price)
names(optimized_prie_bad)<-c('Optimized Price','Change in Cost')
```

Plot the optimal price for selling the car seats at those stores where the shelve location is good and bad
```{r}
a<-ggplot(optimized_price_good, aes(optimized_price_good$`Optimized Price`, optimized_price_good$`Change in Cost`, colour='Good location')  ) + labs(title = 'Optimized Price VS Cost Price',x='Optimized price',y='Cost Price') + geom_line() +  scale_color_manual("", values = ("Good Price'" = "green")) +geom_point(colour='black')
```

```{r}
b<-ggplot(optimized_prie_bad, aes(optimized_prie_bad$`Optimized Price`, optimized_prie_bad$`Change in Cost`, colour='bad location ')  ) + labs(x='Optimized price',y='Cost Price') + geom_line() +  scale_color_manual("", values = ("bad Price'" = "red")) +geom_point(colour='black')
grid.arrange(a, b, ncol=1)
```

From the above graph optimized price changes withrespect to cost price by considering the shelve location

When production cost is 55 and shelve location is good the optimized price is 109.07

When production cost is 55 and shelve location is bad the optimized price is 79.64
